Visually pleasing knot projections

### 2021-09-28 inst/jma_rebuttal.tex

Fig. 10: Why is the absence of mirror symmetry pointed out here?

\textcolor{blue}{Some knots have dihedral symmetry but not this one.
  Discussion added.}

@@

\section*{Detailed rebuttal: Reviewer \#2}

This lovely article addresses the interesting question of
how to produce pleasing and informative images of two dimensional knot
diagrams. In addition to the discussion it describes how to use a
combination of the software packages Inkscape and R to optimise knots.

At the moment, however the paper is a little too close to simply being
a software manual for the software, and needs in particular to
describe the techniques used by the software to create the optimised
images.%issue35<

\textcolor{blue}{I think this is a perfectly reasonable comment for
  the original manuscript.  I believe the revision is a very much
  improved document.}

@@

In addition there is a rather consistent use of absolute terms for
pleasing vs ugly knots. Aesthetics is a complex field, but generally
does not provide strong answers.

\textcolor{blue}{Absolute terms now rephrased more carefully.}%issue#36

While the choices made in this paper
are reasonable, they are simply stated, rather than including a
justification for why they are chosen. They certainly only apply to a
particular knid of knot diagram. This can be see in the final image
showing all the knots with up to 8 crossings. While some of the
resulting diagrams are beautiful, I particularly enjoyed {\tt 8\_10}
and {\tt 8\_17}, some are not so pleasing to me. In particular the
algorithm given likes to over-tighten when the line wraps round
itself. This can be seen particularly in {\tt 8\_3}, but also in {\tt
  8\_5}, {\tt 8\_6} and {\tt 8\_11}. This is itself a personal
preference not an absolute, but a discussion of how to adjust the
set-up of the software to make personal aesthetic choices would
strengthen the paper.

\textcolor{blue}{This is indeed an insightful comment.  My original
  view was that there was a single set of weightings for the various
  badnesses, that most people would agree upon; and my task as
  software engineer was to find the projection that optimizes these
  standard weightings.\\ \\ Reflecting on the referee's comment, I
  realise with a shock that my weightings do not reflect some
  universal ideal.  Rather, my choice of weightings are as subjective
  as any other aspect of the software and, as such, are peculiar to
  me.  This is obvious in retrospect but was not clear to me at all
  until just now.\\ \\ One of the benefits of the {\tt knotR} software
  is that it allows this kind of conversation to occur; I have added a
  discussion to the manuscript, just before the conclusions section.
  There, I present projections of $8_3$ but with different penalties
  for angle crossing terms.  We see the results and can compare like
  with like, perhaps coming to a deeper understanding of pleasingness
  of projections in the process.\\ \\}

@@

1) Conduct a thorough literature review of work on the creation of
knot diagrams and their aesthetics and place this paper into that
context as well as the broader context of optimisation in art. % issue~#39

\textcolor{blue}{I have added a literature review as suggested that
  discusses knot diagrams from early Celtic artwork through to
  mathematica.\\ \\ The referee makes the perfectly reasonable
  suggestion of discussing the broader context of optimization of art.
  I will address this comment colloquially.  It is obvious to me, and
  clearly to the referee as well, that numerical optimization
  techniques are well-suited to ``rounding off rough edges'' from a
  wide range of applications; and further that numerical optimization
  will produce ``nice looking'' results.  I have cited some of the
  more prominent workers in the field, whose work is closest to 2D
  knot projections.}

2) Include a discussion of why the aesthetic choices made for the
optimisation are pleasing as well as how to adjust the methodology in
order to make different personal choices. It might even be interesting
to develop some distinct styles of diagrams (by changing the ``badness"
function, and use the methods to create optimised images for each
style.

\textcolor{blue}{I have included a figure that compares a knot with
  two different weightings}

@@

3) Give basic information about the specific methods being used for
the optimisation rather than just using the function given in R as a
black box.

\textcolor{blue}{Brief discussion added: the package includes
  Nelder-Mead by default but the user has the option to use a
  Newton-type method.}

### 2021-09-28 inst/jma_knot.tex
spelling check

Knot diagrams are ubiquitous in the modern discipline of mathematical
knot theory.  In the nineteeth century we see Tait~\cite{tait1884}
publishing an early systematic study of knots including a beautiful
plate of elegantly hand-drawn cursive knot diagrams.  The tradition
continues into the twentieth century with Rolfsen~\cite{rolfsen1976}
presenting an appendix containing many knot and link projections.
Rolfsen's diagrams are used widely today: Adams~\cite{adams2004}
reproduces his work extensively, as do many more recent works.

@@

The R programming language~\cite{rcore2021}, while usually associated
with statistical analysis and data processing, is also a suitable tool
for producing visually attractive images.  Generative art [that is,
  use of an algorithm, with or without a random component, in a
  creative process] is possible in R~\cite{brunner2021}.  More
specificially to knot theory, the {\tt Rknots}
package\cite{comoglio2011,comoglio2016} presents software for folded
protein structures, and includes 3D renderings of commonly encountered
knotted strands.

@@

Here, knot paths are required to have Bezier handles that are
symmetrically placed with regard to nodes (this is a user-settable
option in inkscape).  One consquence of this design choice is that
radius of curvature is not matched exactly across a node; the path is
not G2 smooth in CAD terminology.  However, if we can ensure that the
radius of curvature changes only by a small amount, visual
continuity---in the sense of absence of visible interruptions to a
smoothly evolving strand---is preserved.  At a crossing point it is
important that both the unbroken and broken strands (designated
``overstrand'' and ``understrand'' respectively) are smooth.  We would
like strand crossing points to be far from nodes, as this ensures
visual continuity of strands at crossing points, especially the
understrand.

@@

There now follows a selection of pleasing knot diagrams taken from
datasets provided with the package, illustrating the relative ease
with which knot diagrams may be created and optimized.
Figure~\ref{perko_AB} shows two forms of a 10-crossing knot once
erroneously considered to be topologically distinct;
figure~\ref{orn20} shows an ornamenntal knot with exact five-fold
symmetry (but not dihedral symmetry); and figure~\ref{all8} shows all
prime knots with eight or fewer crossings, following
Rolfsen~\cite{rolfsen1976}.  The package includes all knots to nine
crossings.

>>>>

Knot diagrams are ubiquitous in the modern discipline of mathematical
knot theory.  In the nineteenth century we see Tait~\cite{tait1884}
publishing an early systematic study of knots including a beautiful
plate of elegantly hand-drawn cursive knot diagrams.  The tradition
continues into the twentieth century with Rolfsen~\cite{rolfsen1976}
presenting an appendix containing many knot and link projections.
Rolfsen's diagrams are used widely today: Adams~\cite{adams2004}
reproduces his work extensively, as do many more recent works.

@@

The R programming language~\cite{rcore2021}, while usually associated
with statistical analysis and data processing, is also a suitable tool
for producing visually attractive images.  Generative art [that is,
  use of an algorithm, with or without a random component, in a
  creative process] is possible in R~\cite{brunner2021}.  More
specifically to knot theory, the {\tt Rknots}
package\cite{comoglio2011,comoglio2016} presents software for folded
protein structures, and includes 3D renderings of commonly encountered
knotted strands.

@@

Here, knot paths are required to have Bezier handles that are
symmetrically placed with regard to nodes (this is a user-settable
option in inkscape).  One consequence of this design choice is that
radius of curvature is not matched exactly across a node; the path is
not G2 smooth in CAD terminology.  However, if we can ensure that the
radius of curvature changes only by a small amount, visual
continuity---in the sense of absence of visible interruptions to a
smoothly evolving strand---is preserved.  At a crossing point it is
important that both the unbroken and broken strands (designated
``overstrand'' and ``understrand'' respectively) are smooth.  We would
like strand crossing points to be far from nodes, as this ensures
visual continuity of strands at crossing points, especially the
understrand.

@@

There now follows a selection of pleasing knot diagrams taken from
datasets provided with the package, illustrating the relative ease
with which knot diagrams may be created and optimized.
Figure~\ref{perko_AB} shows two forms of a 10-crossing knot once
erroneously considered to be topologically distinct;
figure~\ref{orn20} shows an ornamental knot with exact five-fold
symmetry (but not dihedral symmetry); and figure~\ref{all8} shows all
prime knots with eight or fewer crossings, following
Rolfsen~\cite{rolfsen1976}.  The package includes all knots to nine
crossings.
